A quantitative framework for investigating the reliability of empirical network construction

### 2018-06-26 manuscript/CI_interactions.tex
adding Tomas comments to main text

\title{A quantitative framework for investigating the reliability of network construction}

@@

    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. For interactions that have not been observed, most data sets will not contain enough information to be confident that unobserved interactions truly did not occur.
    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction. We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge. We illustrate this framework using the most extensively sampled network to date. 
    \item We found significant uncertainty in estimates for the probability of most pairwise interactions which we could, however, limit with informative priors. This uncertainty scaled up to summary measures of network structure such as connectance or nestedness. Even with informative priors, our results suggest that the extremely well-sampled network we use as a test case is missing many interactions that may occur rarely or under different local conditions. 
    \item Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 350 words for MEE. This is 270 exactly.
\end{enumerate}

@@

    Representing an ecological community as a network offers a convenient summary of how the community is constructed as networks simultaneously describe species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered static representations of the communities they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a} while interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Moreover, variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

@@

    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could be expanded to deal with interaction frequencies and strength. To define the problem, we will first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. 
    % Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web and, finally, illustrate this framework using an extensively sampled empirical network.
    % We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

@@

    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed. Say a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

@@

      When using an informative prior, it is important to ensure that the prior accurately reflects the focal  system. For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species wtih a set of closely-related insects. The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others. Trait differences between species mean that a species-species network will likely contain fewer interactions than a genotype-species network. Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.

      The choice of prior will depend on the information available. In general, it is best to use a prior taken from a similar system. If such data are not available, a prior based on many networks systems with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data"). If there is no suitable informative prior, it is best to use an explicitly uninformative prior. While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.

@@

      We illustrate the process of constructing a Bayesian network using the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S3} for details).

      The high spatiotemporal resolution and unusally high sampling effort of this dataset make this it particularly well suited for illustrating the difficulties in completely sampling a network. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).

@@

        A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand. If such data are not available, one might instead use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S5}).

        To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S7}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

@@

      Researchers usually use interaction matrices as a tool to calculate measures of network structure. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results. One way to avoid this situation is to calculate the properties of a suite of simulated networks.

@@

  We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49. Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008. When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

  For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}). The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}). To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

  We found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D). Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter the farther apart were the observed and posterior webs.

@@

  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring. In such cases, an informative prior distribution gives us more reasonable estimates of interaciton probabilities than assuming all unobserved interactions cannot occur. This approach will also be useful when considering interactions involving species entering new ranges due to climate change or introductions. Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

  Our results also demonstrate how incomplete detection of interactions scales up to affect network structure. The structure of our well-sampled, replicated observed network is most similar to the structure of networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities. Acknowledging the uncertainty inherent in a description of a system that is missing up to half of the feasible interactions is vital if we are to compare structures across systems, link structure to stability, etc.

  Based on the framework described above, we offer some recommendations for improved descriptions of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate these recommendations, we provide all code used in this paper in the supplementary material.

@@

  \begin{figure}[h!]
      \caption{Despite the high levels of replicaiton in our example dataset, most galler-natural enemy pairs were never observed co-occurring, and those that did co-occur were rarely observed interacting. \textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once; the 9794 galler-enemy pairs that were never observed co-occurring are omitted.
      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \begin{center}
      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      \end{center}
      \end{figure}

>>>>

\title{A quantitative framework for investigating the reliability of empirical network construction}

@@

    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. For interactions that have not been observed, most data sets will not contain enough information for the ecologist to be confident that unobserved interactions truly did not occur.
    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction. We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge. We illustrate this framework using the most extensively sampled network to date. 
    \item We found significant uncertainty in estimates for the probability of most pairwise interactions. This uncertainty can, however, be constrained with informative priors. This uncertainty scaled up to summary measures of network structure such as connectance or nestedness. By using an extremely well-sampled network as a test case, we find that even with informative priors we are likely to miss many interactions that may occur rarely or under different local conditions. 
    \item Overall, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies and the utility of treating interactions as probabilities in pinpointing areas where more study is needed. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 350 words for MEE. This is 290 exactly.
\end{enumerate}

@@

    Representing an ecological community as a network offers a convenient summary of how it is constructed since networks simultaneously describe species composition and interactions between species. A tabulation of the nodes (species) and their relative abundances forms the basis for traditional metrics of community composition such as alpha diversity. A network framework combines this tabulation of nodes with a list of interactions (links between nodes) so that networks provide additional, higher-order information on community structure. Despite this additional information, empirical descriptions of ecological networks are still limited because they are usually considered static representations of the communities they describe. That is, whether the network is assembled based on aggregated data, a single intensive ``snapshot" sample, or expert knowledge, interactions are assumed to occur deterministically wherever and whenever the community is observed~\citep{Olesen2011a}.

    The assumption of static communities contrasts with the known stochasticity of ecological communities~\citep{Gotelli2000}. Community composition and species abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012}, time~\citep{Kitching1987,Olesen2011a}, and between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}. Moreover, variability in community composition and interactions may or may not be closely related. The removal of a species from a site will obviously also remove its interactions but, conversely, the co-occurrence of potentially interacting species does not guarantee that the species will interact at a given place and time. Interactions can be lost if the interaction partners remain present but are separated in time or are too rare to detect each other~\citep{Tylianakis2010}. Interactions can also fail to occur because of environmental contingencies~\citep{Poisot2015}, or through changes to individual preferences~\citep{Fodrie2015}.

@@

    In this study, we formalise the description of interactions between species as probabilities and develop analytical tools to capture the uncertainty in the estimation of these interactions. We focus on binary interactions as a first step, but the framework could later be expanded to deal with interaction frequencies and strength. To define the problem, we will first identify the different contributions to the uncertainty of an interaction and discuss the implications of each source of uncertainty for the properties of ecological networks. 
    % Next, we develop an analytical framework to quantify the uncertainty around interactions in an empirical web and, finally, illustrate this framework using an extensively sampled empirical network.
    % We illustrate this framework using the most extensively sampled network to date (Box 1).  Finally, we offer tangible recommendations for improved descriptors of ecological interactions. Through these efforts, we demonstrate both the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies.

@@

    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for interactions that have not been observed. Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

@@

      When using an informative prior, it is important to ensure that this prior accurately reflects the focal  system. For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species with a set of closely-related insects. The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others. Trait differences between species mean that a species-species network will likely contain fewer interactions than a genotype-species network. Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.

      The choice of prior will depend on the information available. In general, it is best to use a prior taken from a similar system as emphasized above. If such data are not available, a prior based on many networks systems with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data"). If there is no suitable informative prior, it is best to use an explicitly uninformative prior. While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.

@@

      To illustrate the process of constructing a Bayesian network, we use the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S3} for details).

      The high spatiotemporal resolution and unusally high sampling effort of this dataset make it particularly well suited for illustrating the difficulties in completely sampling a network. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for brevity, present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).

@@

        To treat each interaction as a Bayesian probability, we will combine the observed data with a distribution based on prior information. A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand. If such data are not available, one might instead use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S5}).

        To obtain priors based on a single sub-network --Zillis in Graub\"{u}nchen, Switzerland-- we estimated frequencies of interactions based on the normalised degree of each species in each network component (see \emph{Appendix S6} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S7}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

@@

      Researchers usually use interaction matrices as a tool to calculate measures of network structure. Computing most network metrics is straightforward when the different $\lambda$ of the adjacency matrix are known and assumed not to vary~\citep{Poisot2016}. Incorporating variance in $\lambda$ into these calculations, however, is not so easy. Computation of these metrics involves non-linear functions. By Jensen's inequality~\citep{Jensen1906}, this means that the average of a network metric (a function of stochastic interactions) is not the same as the network metric calculated based on the average interaction probability. Any uncertainty in the values of $\lambda$ could bias both the mean and variance of network metrics, giving misleading results. One way to avoid this situation is to calculate the properties of a suite of simulated networks.

@@

  We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49. Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008. When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. This distributions is very close to 0 with small variance about $\lambda$; if species $i$ and $j$ co-occurred 374 times without interacting, they   are extremely unlikely to do so at other sites or times.

  For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}). The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}). To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively. Note that these are relatively large sample sizes compared to currently-available empirical networks~\citep{Morris2014}.

  Scaling up to network structure, we found that the connectance, mean links per galler, and mean links per natural enemy were much lower in the observed web (C=0.078, $L_{galler}$=9.99, and $L_{natural enemy}$=7.45, respectively) than in the posterior webs (0.186 $\leq$ C $\leq$ 0.198, 13.4 $\leq L_{galler} \leq$ 14.6, and 23.4 $\leq L_{natural enemy} \leq$ 25.0). When the detection probability was relatively low (i.e., 50\%), however, the properties of randomised networks became similar to those in the observed webs (Fig.~\ref{posterior_webs}A,B,D). Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig.~\ref{posterior_webs}C); in this case, the stronger the detection filter, the farther apart were the observed and posterior webs. In general, the observed network is most similar to simulated networks where only half of the plausible links are detected.

@@

  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to set appropriate bounds on interaction probabilities for species which were rarely or never observed co-occurring. In such cases, an informative prior distribution gives us more reasonable estimates of interacition probabilities than assuming that no unobserved interactions can ever occur. This approach will also be useful when considering interactions involving species entering new ranges due to climate change or introductions. Understanding these species' interactions is important for a variety of conservation questions, and a Bayesian approach using a trait-matching model or data from species' current ranges could help us to anticipate how species will integrate into new communities.

  Our results also demonstrate how incomplete detection of interactions scales up to affect network structure. The structure of the well-sampled network used in our case study is most similar to the structure of simulated networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities. If our descriptions of empirical systems are missing up to half of the feasible interactions, then it is vital to acknowledge this inherent uncertainty before comparing structures across systems or relating structure to stability.

  Based on the framework described above, we can now offer some recommendations for improved descriptions of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, where sampling on the order of 30-50 observations per species pair is not possible (i.e., in most cases), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate the practical application of these recommendations, we provide all code used in this paper in the supplementary material.

@@

  \begin{figure}[h!]
      \caption{Despite the high levels of replication in our empirical dataset, most galler-natural enemy pairs were never observed co-occurring, and those that did co-occur were rarely observed interacting. \textbf{A)} Here we show a histogram of the number of pairs of species observed co-occurring at least once; the 9794 galler-enemy pairs that were never observed co-occurring are omitted.
      \textbf{B)} Here we show a histogram of the number of observed interactions within pairs of co-occurring species. Species which co-occurred but never interacted are included. 
      \textbf{C)} Here we show, for each species pair, the number of observed interactions plotted against the number of observed co-occurrences. The red, dashed line indicates a 1:1 relationship between interactions and co-occurrences.}
      \label{histograms}
      \begin{center}
      \includegraphics*[height=.6\textheight]{figures/GP_histogram.eps}
      \end{center}
      \end{figure}
